---
title: "Lab 07 - Conveying the right message through visualisation"
author: "Lilly McClendon"
date: "02-28-2025"
output: github_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercise 1

```{r create-kansas-data-frame}
df <- tribble(
  ~date, ~count, ~mask,
 "7/12/2020", 25.2, "mask", 
 "7/12/2020", 9.8, "no mask",
 "7/13/2020", 19.8, "mask",
 "7/13/2020", 9.0, "no mask", 
 "7/14/2020", 19.7, "mask", 
 "7/14/2020", 8.5, "no mask",
 "7/15/2020", 20.5, "mask",
 "7/15/2020", 9.8, "no mask", 
 "7/16/2020", 19.8, "mask", 
 "7/16/2020", 9.9, "no mask",
 "7/17/2020", 19.85, "mask",
 "7/17/2020", 9.5, "no mask", 
 "7/18/2020", 20.5, "mask", 
 "7/18/2020", 9.5, "no mask",
 "7/19/2020", 19.9, "mask",
 "7/19/2020", 9.0, "no mask", 
 "7/20/2020", 20.5, "mask", 
 "7/20/2020", 8.5, "no mask",
 "7/21/2020", 21.25, "mask",
 "7/21/2020", 8.5, "no mask", 
 "7/22/2020", 19.9, "mask", 
 "7/22/2020", 8.6, "no mask",
 "7/23/2020", 19.9, "mask",
 "7/23/2020", 8.3, "no mask", 
 "7/24/2020", 20.5, "mask", 
 "7/24/2020", 9.9, "no mask",
 "7/25/2020", 19.0, "mask",
 "7/25/2020", 9.95, "no mask", 
 "7/26/2020", 19.3, "mask", 
 "7/26/2020", 10.1, "no mask",
 "7/27/2020", 17.0, "mask",
 "7/27/2020", 9.5, "no mask",
 "7/28/2020", 16.2, "mask",
 "7/28/2020", 9.55, "no mask",
 "7/29/2020", 16.3, "mask",
 "7/29/2020", 9.6, "no mask",
 "7/30/2020", 16.5, "mask", 
 "7/30/2020", 10.0, "no mask",
 "7/31/2020", 16.0, "mask",
 "7/31/2020", 8.8, "no mask",
 "8/1/2020", 16.1, "mask",
 "8/1/2020", 9.0, "no mask",
 "8/2/2020", 15.8, "mask",
 "8/2/2020", 8.85, "no mask",
 "8/3/2020", 15.9, "mask",
 "8/3/2020", 9.3, "no mask",
)
```

### Exercise 2

```{r kansas-data-new-visualization}
library(ggplot2)
ggplot(df, aes(x = date, y = count, group = mask, color = mask)) +
  geom_line() + 
  labs(title = "New Visualization of Kansas Covid-19 Average of Daily Cases Per 100,000", subtitle = "Mask Mandate Counties vs. No Mask Mandate Counties", caption = "Source: Kansas Department of Health and Environment", x = "Date", y = "Average Daily Cases Per 100,000") + 
  scale_color_manual(values=c('darkblue', 'darkred')) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  theme(plot.title = element_text(hjust=0.5))
```

### Exercise 3 

In my new visualization, I plotted both the Mask Mandate counties and No Mask Mandate counties on the same y-axis scale. Because they are both on the same scale, they are much easier to compare. In my visualization it is much clearer that in this data set, counties with mask mandate had a higher number of average daily Covid-19 cases than counties without mask mandates. In the original visualization, it seemed that for most of July there wasn't much of a difference in average daily cases between mask mandate counties and no mask mandate counties and towards the end of July and early August, there was a much lower number of average daily Covid-19 cases than counties without a mask mandate. 




