---
title: "Lab 07 - Conveying the right message through visualisation"
author: "Lilly McClendon"
date: "02-28-2025"
output: github_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercise 1

```{r create-kansas-data-frame}
df <- tribble(
  ~date, ~count, ~mask,
 "7/12/2020", 25.2, "mask", 
 "7/12/2020", 9.8, "no mask",
 "7/13/2020", 19.8, "mask",
 "7/13/2020", 9.0, "no mask", 
 "7/14/2020", 19.7, "mask", 
 "7/14/2020", 8.5, "no mask",
 "7/15/2020", 20.5, "mask",
 "7/15/2020", 9.8, "no mask", 
 "7/16/2020", 19.8, "mask", 
 "7/16/2020", 9.9, "no mask",
 "7/17/2020", 19.85, "mask",
 "7/17/2020", 9.5, "no mask", 
 "7/18/2020", 20.5, "mask", 
 "7/18/2020", 9.5, "no mask",
 "7/19/2020", 19.9, "mask",
 "7/19/2020", 9.0, "no mask", 
 "7/20/2020", 20.5, "mask", 
 "7/20/2020", 8.5, "no mask",
 "7/21/2020", 21.25, "mask",
 "7/21/2020", 8.5, "no mask", 
 "7/22/2020", 19.9, "mask", 
 "7/22/2020", 8.6, "no mask",
 "7/23/2020", 19.9, "mask",
 "7/23/2020", 8.3, "no mask", 
 "7/24/2020", 20.5, "mask", 
 "7/24/2020", 9.9, "no mask",
 "7/25/2020", 19.0, "mask",
 "7/25/2020", 9.95, "no mask", 
 "7/26/2020", 19.3, "mask", 
 "7/26/2020", 10.1, "no mask",
 "7/27/2020", 17.0, "mask",
 "7/27/2020", 9.5, "no mask",
 "7/28/2020", 16.2, "mask",
 "7/28/2020", 9.55, "no mask",
 "7/29/2020", 16.3, "mask",
 "7/29/2020", 9.6, "no mask",
 "7/30/2020", 16.5, "mask", 
 "7/30/2020", 10.0, "no mask",
 "7/31/2020", 16.0, "mask",
 "7/31/2020", 8.8, "no mask",
 "8/1/2020", 16.1, "mask",
 "8/1/2020", 9.0, "no mask",
 "8/2/2020", 15.8, "mask",
 "8/2/2020", 8.85, "no mask",
 "8/3/2020", 15.9, "mask",
 "8/3/2020", 9.3, "no mask",
)
```

### Exercise 2

```{r kansas-data-new-visualization}
library(ggplot2)
ggplot(df, aes(x = date, y = count, group = mask, color = mask)) +
  geom_line() + 
  labs(title = "New Visualization of Kansas Covid-19 Average of Daily Cases Per 100,000", subtitle = "Mask Mandate Counties vs. No Mask Mandate Counties", caption = "Source: Kansas Department of Health and Environment", x = "Date", y = "Average Daily Cases Per 100,000") + 
  scale_color_manual(values=c('darkblue', 'darkred')) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  theme(plot.title = element_text(hjust=0.5))
```

### Exercise 3 

In my new visualization, I plotted both the Mask Mandate counties and No Mask Mandate counties on the same y-axis scale. Because they are both on the same scale, they are much easier to compare. In my visualization it is much clearer that in this data set, counties with mask mandate had a higher number of average daily Covid-19 cases than counties without mask mandates. In the original visualization, it seemed that for most of July there wasn't much of a difference in average daily cases between mask mandate counties and no mask mandate counties and towards the end of July and early August, there was a much lower number of average daily Covid-19 cases than counties without a mask mandate. 

### Exercise 4

This visualization tells us that in this data set there were fewer average daily cases of Covid-19 in no mask mandate counties than mask mandate counties. This does not line up with what I know about mask wearing, however this was an observational study which may be subjected to potential confounds. It may be that masks are protective of Covid-19, but other variables obscured these effects in the current data. 

### Exercise 5 

The factors from my accurate visualization regarding mask-wearing and COVID-19 that reflect the actual message conveyed by the data is that the scale of the axes is the same for both the mask mandate counties and the no-mask mandate counties. This makes it easier to visual compare because in the original visualization, for the mask wearing counties 25 
per 100,000 is the same location as 14 per 100,000 for the no-mask wearing counties. So when just looking at the visualization overall and not specifically at the axes, it easily seems as though there are similar or fewer cases of COVID-19 for the mask mandate counties compared to the no mask mandate counties. The line graph also allows the data to be shown day by day and how the trends change. Also, using the cases per 100,000 as a variable is helpful in conveying the accurate method because it allows for direct comparison between the two counties even if they have different total populations. 


